Sandbox BC Data

### 2020-11-16 scripts/draft_play.Rmd
Showing the cornflower blue for you...

```
```{r}
#this is more in line with the BC graphing
#ggplot(fresh_primo, aes(year, frequency))+
# geom_smooth(color = "cornflowerblue") +
# theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#  facet_wrap(~disability)

>>>>

```
```{r}
#this is more in line with the BC graphing
ggplot(fresh_primo, aes(year, frequency))+
 geom_smooth(color = "cornflowerblue") +
 theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
 facet_wrap(~disability)
